---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(ProjectApriori)
```

# ProjectApriori

The goal of ProjectApriori is to create association rules of type X=>Y by using the apriori algorithm.

## Installation

You can install ProjectApriori from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("TimToebrock/Project_Apriori")
```

## Example

This is a basic example which shows you how to create association rules with Rpriori using the "Groceries" dataset:

```{r example, warning=FALSE}
data("Groceries")
Rules <- AssociationRules(Itemsets=Groceries, minsupport = 0.01, minconfidence = 0)
show(Rules)
```

To create rules you need to specifiy an transactions databse and a minimum support threshold but you can also set a minimum confidence
threshold.

## Inspecting the data

To get summary statistics on the rules simply call summary()
```{r}
summary(Rules)
```


If you want to take a look at the underlying data used in rule creation there are multiple ways. One way is:
```{r}
Frequent <- extract(Rules)
summary(Frequent)
```
This extracts the frequent itemsets used to calculate association rules. You can also create a frequent itemmatrix directly:
```{r}
Frequent2 <- FindFrequentItemsets(Groceries, 0.01)
```



If you want to take a look at the transactionsmatrix used to calculate the frequent items you need to create an object first:
```{r}
Transactions <- makeTAMatrix(Groceries)
summary(Transactions)
```


